R dyntrace report

### 2018-04-03 graphs/report-basic-info.Rmd
Report: two analyses in separation. Cast integer to numeric.

basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

top5_basic_info <- 
  basic_info %>% 
  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)

aggregate_basic_info <- 
  basic_info %>% summarise(
    name="*",
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=(aggregated_functions %>% count %>% pull(n)),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

missing_basic_info <- 
  basic_info %>% summarise(
    name="...",
    datasets="...",
    n.datasets="...",
    n.functions="...",
    n.calls="...",
    n.promises="...",
    n.promise.forces="...",
    n.promise.lookups="...", 
    n.alien.promises="...",
    n.alien.promise.forces="..."
  )

 n.packages <- basic_info %>% count %>% pull(n)

 # some graphical stuff
 package_figure_width <- 10
 package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
 package_figure_rows <- ceiling(n.packages/package_figure_columns)
 package_figure_height <- ceiling(10/7 * package_figure_rows)
```

@@

```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
```

@@

``` {r, "overview", echo=FALSE, warning=FALSE}
union(top5_basic_info, aggregate_basic_info) %>% 
  mutate(
    n.functions=pp_trunc(n.functions), 
    n.calls=pp_trunc(n.calls), 
    n.promises=pp_trunc(n.promises), 
    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
    n.promise.forces=pp_trunc(n.promise.forces),
    n.promise.lookups=pp_trunc(n.promise.lookups)
  ) %>% 
  select(name, n.functions, n.calls, n.promises, 
         n.promise.accesses, n.promise.forces, 
         n.promise.lookups) %>%  
  kable(col.names=c("package", "functions", "calls", "promises",
                    "promise accesses", "promise forces",
                    "promise lookups"), align="lrrrrrr")
```

>>>>

#basic_info <- 
#  load_local_csv("basic_info.csv") %>%
#  group_by(name) %>%
#  summarise(
#    datasets=paste(name, collapse=", "),
#    n.datasets=n(),
#    n.functions=sum(n.functions),
#    n.calls=sum(n.calls),
#    n.promises=sum(n.promises),
#    n.promise.forces=sum(n.promise.forces),
#    n.promise.lookups=sum(n.promise.lookups), 
#    n.alien.promises=sum(n.alien.promises),
#    n.alien.promise.forces=sum(n.alien.promise.forces)
#  )

# top5_basic_info <- 
#   basic_info %>% 
#   arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)
# 
# aggregate_basic_info <- 
#   basic_info %>% summarise(
#     name="*",
#     datasets=paste(name, collapse=", "),
#     n.datasets=n(),
#     n.functions=(aggregated_functions %>% count %>% pull(n)),
#     n.calls=sum(n.calls),
#     n.promises=sum(n.promises),
#     n.promise.forces=sum(n.promise.forces),
#     n.promise.lookups=sum(n.promise.lookups), 
#     n.alien.promises=sum(n.alien.promises),
#     n.alien.promise.forces=sum(n.alien.promise.forces)
#   )
# 
# missing_basic_info <- 
#   basic_info %>% summarise(
#     name="...",
#     datasets="...",
#     n.datasets="...",
#     n.functions="...",
#     n.calls="...",
#     n.promises="...",
#     n.promise.forces="...",
#     n.promise.lookups="...", 
#     n.alien.promises="...",
#     n.alien.promise.forces="..."
#   )
#
# n.packages <- basic_info %>% count %>% pull(n)
# 
# # some graphical stuff
# package_figure_width <- 10
# package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
# package_figure_rows <- ceiling(n.packages/package_figure_columns)
# package_figure_height <- ceiling(10/7 * package_figure_rows)
```

@@

```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
#basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
```

@@

``` {r, "overview", echo=FALSE, warning=FALSE}
#union(top5_basic_info, aggregate_basic_info) %>% 
#  mutate(
#    n.functions=pp_trunc(n.functions), 
#    n.calls=pp_trunc(n.calls), 
#    n.promises=pp_trunc(n.promises), 
#    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
#    n.promise.forces=pp_trunc(n.promise.forces),
#    n.promise.lookups=pp_trunc(n.promise.lookups)
#  ) %>% 
#  select(name, n.functions, n.calls, n.promises, 
#         n.promise.accesses, n.promise.forces, 
#         n.promise.lookups) %>%  
#  kable(col.names=c("package", "functions", "calls", "promises",
#                    "promise accesses", "promise forces",
#                    "promise lookups"), align="lrrrrrr")
```
